---
title: "Tidy Tuesday #1"
author: "College Tuition"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

# Code

## {.tabset .tabset-fade}

### Setup

```{r setup, message=F}
remove(list = ls(all.names = TRUE))

detachAllPackages <- function() {
  basic.packages.blank <-  c("stats","graphics","grDevices","utils","datasets","methods","base")
  basic.packages <- paste("package:", basic.packages.blank, sep = "")
  package.list <- search()[ifelse(unlist(gregexpr("package:", search())) == 1,TRUE,FALSE)]
  package.list <- setdiff(package.list, basic.packages)
  if (length(package.list) > 0)  for (package in package.list) {
    detach(package, character.only = TRUE)}}

detachAllPackages()

knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, dpi = 144, fig.align = "center")

computeComments = function(...) return(x[1])
```

```{r, echo=T, message=F, warning=F}
if (!require(pacman)) {
  install.packages("pacman")
  require(pacman)
}

p_load(lubridate, timetk, tidyverse, knitr, ggthemes, httr, noncensus, cowplot, readxl, flexdashboard)

p_load_gh("hrbrmstr/hrbrthemes","jbkunst/highcharter")

data("states")

path <- "https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/us_avg_tuition.xlsx"

GET(path, write_disk(tf <- tempfile(fileext = ".xlsx")))
```

### Manipulation

```{r echo=T}
dat <- read_excel(tf) %>%
  mutate(Divsion = states[match(State, states$name), 4],
         Region  = states[match(State, states$name), 3],
         State   = states[match(State, states$name), 1]) %>%
  gather(Year, Tuition, -c(State, Region, Divsion)) %>%
  mutate(Year = as.numeric(gsub("-.*", "", Year))) %>%
  mutate_if(is.numeric, round, digits=3) %>%
  {.}

unlink(tf)
```

### Plotting

ggplot2:

```{r echo=T, message=F, warning=F}
st_plt <- function(df, divsion) {
  df %>%
    filter(Divsion == divsion) %>%
    ggplot(aes(Year, Tuition, color = State, fill = State)) +
    geom_line(stat = "identity", size = .7) +
    theme_ipsum_rc() + 
    ylim(c(3500,15500)) +
    coord_fixed(ratio = .00065) +
    xlab("") + ylab("")
}

plist <- lapply(levels(dat$Divsion), 
                FUN = function(x) {st_plt(dat,x)})
```

highcharter:

```{r echo=T}
hc_st_plt <- function(df, divsion) {
  df %>%
    filter(Divsion == divsion) %>%
    hchart("spline", hcaes(x = Year, y = Tuition, group = State)) %>%
    hc_tooltip(crosshairs = TRUE, shared = TRUE)
}
```

```{r, echo=F}
x <- levels(dat$Divsion)
y <- 1
```

# `r x[1]` {data-navmenu="ggplot2 - Select a Region"}

### 

```{r, echo=F}
comments = computeComments()
valueBox(comments, caption = paste("Average Tuition by State -", "ggplot2", packageVersion("ggplot2")))
```

### 

```{r, echo=F}
print(plist[[y]])

x <- x[-1]
y <- y + 1
```

# `r x[1]` {data-navmenu="ggplot2 - Select a Region"}

### 

```{r, echo=F}
comments = computeComments()
valueBox(comments, caption = paste("Average Tuition by State -", "ggplot2", packageVersion("ggplot2")))
```

### 

```{r, echo=F}
print(plist[[y]])

x <- x[-1]
y <- y + 1
```

# `r x[1]` {data-navmenu="ggplot2 - Select a Region"}

### 

```{r, echo=F}
comments = computeComments()
valueBox(comments, caption = paste("Average Tuition by State -", "ggplot2", packageVersion("ggplot2")))
```

### 

```{r, echo=F}
print(plist[[y]])

x <- x[-1]
y <- y + 1
```

# `r x[1]` {data-navmenu="ggplot2 - Select a Region"}

### 

```{r, echo=F}
comments = computeComments()
valueBox(comments, caption = paste("Average Tuition by State -", "ggplot2", packageVersion("ggplot2")))
```

### 

```{r, echo=F}
print(plist[[y]])

x <- x[-1]
y <- y + 1
```

# `r x[1]` {data-navmenu="ggplot2 - Select a Region"}

### 

```{r, echo=F}
comments = computeComments()
valueBox(comments, caption = paste("Average Tuition by State -", "ggplot2", packageVersion("ggplot2")))
```

### 

```{r, echo=F}
print(plist[[y]])

x <- x[-1]
y <- y + 1
```

# `r x[1]` {data-navmenu="ggplot2 - Select a Region"}

### 

```{r, echo=F}
comments = computeComments()
valueBox(comments, caption = paste("Average Tuition by State -", "ggplot2", packageVersion("ggplot2")))
```

### 

```{r, echo=F}
print(plist[[y]])

x <- x[-1]
y <- y + 1
```

# `r x[1]` {data-navmenu="ggplot2 - Select a Region"}

### 

```{r, echo=F}
comments = computeComments()
valueBox(comments, caption = paste("Average Tuition by State -", "ggplot2", packageVersion("ggplot2")))
```

### 

```{r, echo=F}
print(plist[[y]])

x <- x[-1]
y <- y + 1
```

# `r x[1]` {data-navmenu="ggplot2 - Select a Region"}

### 

```{r, echo=F}
comments = computeComments()
valueBox(comments, caption = paste("Average Tuition by State -", "ggplot2", packageVersion("ggplot2")))
```

### 

```{r, echo=F}
print(plist[[y]])

x <- x[-1]
y <- y + 1
```

# `r x[1]` {data-navmenu="ggplot2 - Select a Region"}

### 

```{r, echo=F}
comments = computeComments()
valueBox(comments, caption = paste("Average Tuition by State -", "ggplot2", packageVersion("ggplot2")))
```

###

```{r, echo=F}
print(plist[[y]])

x <- levels(dat$Divsion)
```

# `r x[1]` {data-navmenu="Highcharter - Select a Region"}

### 

```{r, echo=F}
comments = computeComments()
valueBox(comments, caption = paste("Average Tuition by State -", "highcharter", packageVersion("highcharter")))
```

### 

```{r, echo=F}
hc_st_plt(dat, x[1])

x <- x[-1]
```

# `r x[1]` {data-navmenu="Highcharter - Select a Region"}

### 

```{r, echo=F}
comments = computeComments()
valueBox(comments, caption = paste("Average Tuition by State -", "highcharter", packageVersion("highcharter")))
```

### 

```{r, echo=F}
hc_st_plt(dat, x[1])

x <- x[-1]
```

# `r x[1]` {data-navmenu="Highcharter - Select a Region"}

### 

```{r, echo=F}
comments = computeComments()
valueBox(comments, caption = paste("Average Tuition by State -", "highcharter", packageVersion("highcharter")))
```

### 

```{r, echo=F}
hc_st_plt(dat, x[1])

x <- x[-1]
```

# `r x[1]` {data-navmenu="Highcharter - Select a Region"}

### 

```{r, echo=F}
comments = computeComments()
valueBox(comments, caption = paste("Average Tuition by State -", "highcharter", packageVersion("highcharter")))
```

### 

```{r, echo=F}
hc_st_plt(dat, x[1])

x <- x[-1]
```

# `r x[1]` {data-navmenu="Highcharter - Select a Region"}

### 

```{r, echo=F}
comments = computeComments()
valueBox(comments, caption = paste("Average Tuition by State -", "highcharter", packageVersion("highcharter")))
```

### 

```{r, echo=F}
hc_st_plt(dat, x[1])

x <- x[-1]
```

# `r x[1]` {data-navmenu="Highcharter - Select a Region"}

### 

```{r, echo=F}
comments = computeComments()
valueBox(comments, caption = paste("Average Tuition by State -", "highcharter", packageVersion("highcharter")))
```

### 

```{r, echo=F}
hc_st_plt(dat, x[1])

x <- x[-1]
```

# `r x[1]` {data-navmenu="Highcharter - Select a Region"}

### 

```{r, echo=F}
comments = computeComments()
valueBox(comments, caption = paste("Average Tuition by State -", "highcharter", packageVersion("highcharter")))
```

### 

```{r, echo=F}
hc_st_plt(dat, x[1])

x <- x[-1]
```

# `r x[1]` {data-navmenu="Highcharter - Select a Region"}

### 

```{r, echo=F}
comments = computeComments()
valueBox(comments, caption = paste("Average Tuition by State -", "highcharter", packageVersion("highcharter")))
```

### 

```{r, echo=F}
hc_st_plt(dat, x[1])

x <- x[-1]
```

# `r x[1]` {data-navmenu="Highcharter - Select a Region"}

### 

```{r, echo=F}
comments = computeComments()
valueBox(comments, caption = paste("Average Tuition by State -", "highcharter", packageVersion("highcharter")))
```

### 

```{r, echo=F}
hc_st_plt(dat, x[1])

x <- x[-1]
```

